\documentclass[../jb_user_manual.tex]{subfiles}

\linespread{1.2}
% Enter packages in main documet, not subfiles
\begin{document}
\begin{flushleft}
Thank you for purchasing the Counterwound Labs' JuiceBox, a useful replacement for a gasoline or diesel generator. This system is designed to be a portable power supply for a variety of applications. This manual is intended to serve as an instruction for the safe and sucsesfull operation of the unit.

\vspace{2mm} 
\noindent 
\textbf{Read this guide before using the Juice Box and save it for future reference.}

\vspace{2mm}
The juice box provides all of the services a traditional generator without outputting fumes or loud noises.

\vspace{3mm}
\leftskip=0cm
\begin{Large}
	\textbf{Topics Covered in the Guide}
\end{Large}


\begin{itemize}
\setlength{\itemindent}{3mm} % indents each item
	\item Benefits and Uses
	\item How to Use
	\item A bunch of Other Stuff
\end{itemize}

\textbf{Features} \break
\begin{itemize}
	\item{Integrated charger with 120 VAC plug}
	\item{Integrated 120 VAC inverter with output wall socket}
	\item{4 Deep Cycle Marine Batteries}
	\item{Durable external casing}
	\item{2000 W (16.5 A) Output Capacity}
	\item{LCD Display with diagnostics}
	\item{Low Power indicator and alarm}
	\item{Fault protection breaker} 

\end{itemize}

\textbf{Description} \break 
The juice box is a portable power supply for use in providing temporary power.  The device contains an integrated charger and 120 VAC inverter, as well as a battery bank consisting of 4 deep cycle marine batteries.  The juice box is capable of supplying power requirements of up to 2000 W (~16.5 A).
 
\textbf{Why use the JuiceBox?} \break 
There are some times that you need power without any outlets in range and a noisy, gas powered generator just won't work. How will you power the sound system at an outdoor wedding without the noise of a generator drowning out the service? This is just one of the many times that having a quiet power supply is invaluable. 

\end{flushleft}
\end{document}